### 2015-09-14 vmcai-2016-tex/abstract.tex
Another pass on abstract and intro

A recent trend in the analysis of object-oriented programs is the
modeling of references as sets of guarded values, enabling multiple
heap shapes to be represented in a single state. A fundamental problem
with using these guarded value sets is the creation of test inputs for
programs accepting symbolic reference input parameters. Although
several solutions have been proposed, none have been proven to be
sound and complete with respect to the properties provable by
generalized symbolic execution (GSE). This work presents a method for
initializing reference inputs in a symbolic input heap using guarded
value sets that exactly preserves GSE semantics. A correctness proof
for the initialization scheme is provided, as well as the results of
an empirical evaluation of a proof-of-concept implementation showing a real increase in the size and number of analyzed heaps compared to existing GSE representations. The
initialization technique can be used to ensure that guarded value set
based symbolic execution engines operate in a provably correct manner
with regards to symbolic references.

>>>>

A recent trend in the analysis of object-oriented programs is the
modeling of references as sets of guarded values, enabling multiple
heap shapes to be represented in a single state. A fundamental problem
with using these guarded value sets is the creation of test inputs for
program analyses that accept symbolic reference input parameters. Although
several solutions have been proposed, none have been proven to be
sound and complete with respect to the properties provable by
generalized symbolic execution (GSE). This work presents a method for
initializing reference inputs in a symbolic input heap using guarded
value sets that exactly preserves GSE semantics. A correctness proof
for the initialization scheme is provided, as well as the results of
an empirical evaluation of a proof-of-concept implementation showing a real increase in the size and number of analyzed heaps compared to existing GSE representations. The
initialization technique can be used to ensure that guarded value set
based symbolic execution engines operate in a provably correct manner
with regards to symbolic references.

### 2015-09-14 vmcai-2016-tex/intro.tex
Another pass on abstract and intro

A common hurdle to using guarded value sets is the treatment of
symbolic heap inputs. For many applications, it is desirable to model
the input heap as unconstrained, with operations over the input
references providing the only means of divining its
structure. Precisely modeling operations on unconstrained heap inputs
is challenging because it requires formulating logical predicates over
an input domain that contains a potentially unbounded number of hidden
references~\cite{Chen:2013,Qu:2011}. Generalized symbolic execution
(\gsetxt{}) methods~\cite{GSE03,Deng:2007} provide an accurate
solution, but they quickly produce an overwhelming number of execution
paths for all but the simplest heap shapes. Efforts to
extend~\gsetxt{} principles to guarded value sets have failed to
produce provably equivalent results \cite{LISTEFFORTS}. Thus, despite
the advantages of using guarded value sets, it remains an open
question how they can be used in symbolic execution to automatically
model all possible program behaviors in the case of an arbitrary input
heap.

The contribution of this work is a symbolic initialization scheme for
uninitialized references in a fully symbolic heap. Where GSE lazily
instantiates uninitialized references to either NULL, a new instance
of the correct type, or an alias to a previously initialized object,
the symbolic initialization in this work creates a guarded value set
expressing all of these eventualities in the same symbolic heap. Where
GSE branches the search space on each choice, symbolic initialization
does not. Symbolic initialization only branches on reference compares,
partitioning the symbolic heap to indicate heaps where the references
alias and heaps where the references do not.

This paper includes a proof that symbolic initialization is sound and
complete with respect to properties provable by GSE. Such a result is
important because it means that symbolic initialization can be used to
create test inputs for other analyses in a way that is provably
correct with regards to GSE: there are no missing heaps and there are
no extra heaps.

A proof-of-concept implementation of symbolic initialization is
reported in this paper. The implementation is for Java in the Java
Pathfinder tool. It demonstrates the efficiency of~\symtxt{}, as
compared to existing~\gsetxt{} methods. The use of the guarded value
sets does require extra interaction with an SMT solver, but the
savings in representing multiple heap shapes in a single
representation overcomes the cost of the solver calls. In fact, the
comparison shows an exponential increase in the number of heaps that
can be analyzed in a set of benchmark examples meaning that other
approaches based on~\gsetxt\ fail to complete.

>>>>

A common hurdle to using guarded value sets is the treatment of
\emph{symbolic} heap inputs. A symbolic heap input refers to a portion of the heap that is yet unconstrained, meaning that it is able to take on any shape. For many applications, such a symbolic heap input is desirable for modeling sets of heaps in the analysis: the operations on the heap discovered in the analysis further constrain the symbolic heap input
structure.

Precisely modeling operations on unconstrained heaps
is challenging because it requires formulating logical predicates over
an input domain that contains a potentially unbounded number of hidden
references~\cite{Chen:2013,Qu:2011}. Generalized symbolic execution
(\gsetxt{}), and its variants, provide an accurate
solution, but they quickly produce an overwhelming number of execution
paths for all but the simplest heap shapes \cite{GSE03,Deng:2007}. Efforts to
extend~\gsetxt{} principles to guarded value sets have failed to
produce provably equivalent results \cite{LISTEFFORTS}. Thus, despite
the advantages of using guarded value sets, it remains an open
question to how they can be used in symbolic execution to automatically
model all possible program behaviors in the case of an arbitrary input
heap.

The contribution of this work is \emph{symbolic initialization} for 
uninitialized references in a fully symbolic heap. Where \gsetxt\ lazily
instantiates uninitialized references to either NULL, a new instance
of the correct type, or an alias to a previously initialized object, \symtxt\ creates a guarded value set
expressing all of these eventualities in a single symbolic heap. Where
\gsetxt\ branches the search space on each choice, \symtxt{} does not. Symbolic initialization only branches on reference compares; thus it creates equivalence classes over heaps and only partitions those classes at compares to indicate heaps where the references
alias and heaps where the references do not.

This paper includes a proof that \symtxt\ is sound and
complete with respect to properties provable by \gsetxt. Such a result is
important because it means that \symtxt\ can be used to
create test inputs for other analyses in a way that is provably
correct with regards to \gsetxt: there are no missing \gsetxt\ heaps and there are
no extra GSE heaps.

A proof-of-concept implementation of symbolic initialization is
reported in this paper. The implementation is for Java in the Java
Pathfinder tool. It demonstrates the efficiency of~\symtxt{}, as
compared to existing~\gsetxt{} methods. Although guarded value
sets require extra interaction with an SMT solver, the
savings in representing multiple heap shapes in a single
structure overcomes the cost of the solver calls. In fact, the
comparison shows an exponential increase in the number of heaps that
can be analyzed in a set of benchmark examples, meaning that other
approaches based on~\gsetxt\ fail to complete in the allotted time.
